Automated topic naming to support cross-project analysis of software maintenance activities

### 2011-03-26 msr/msr2011.tex
latest edits

Using our three word-lists (\textsf{exp1}, \textsf{exp2}, \textsf{exp3}), we labeled our topics with an NFR where there was a match between a word in the list and the same word somewhere in the distribution of words that constitute the topic.
A \emph{named topic} is a topic with a matching NFR label. Unnamed
topics occur where there is no such match, which may indicate either a lack of precision, or simply that this topic is not associated with non-functional requirements.
All experiments were run on MaxDB 7.500 and MySQL 3.23 data. LDA
extracted 20 topics per period for each project.
% Is this good enough
This labelling is \emph{semi-unsupervised} because the corpus is not derived from 
the project being labelled, and we did not label the project's topics
ourselves for a training set. The motivation behind this technique is that
because most software often addresses similar issues, we can use the
domain knowledge of software to label relevant topics.
%\todo[inline]{Neil does this explain the unsupervised aspect well enough?}

@@

% was best performing
For \textsf{exp1} the labels with the most topics
were
%labels, those with the most topics, 
\emph{correctness} (182 topics) and \emph{testability} (121). 
We did not get good results for \emph{usability} or \emph{accuracy}, which were associated with fewer than ten topics. 
We also looked for correlation between our labels: excluding double matches (self-correlation), our highest co-occurring terms were \emph{verifiability} with \emph{traceability}, and \emph{testability} with \emph{correctness} (76 and 62 matches, respectively).
% See the following sections for our error analysis.

@@

For \textsf{exp3}, we generally labelled more topics. 
As we mentioned, the word-lists are broad, so there are likely to be false-positives (discussed below). 
We found a high of 265 topics for \emph{usability}, with a low of 44 topics for \emph{maintainability}. 
Common co-occurrences were \emph{reliability} with \emph{usability}, \emph{efficiency} with \emph{reliability}, and \emph{efficiency} with \emph{usability} (200, 190, and 150 topics in common, respectively).

@@

\begin{figure*}[t]
  \centering
 \includegraphics[width=0.8\textwidth]{figures/unsupervised-bar}
 \caption{Performance, ROC values (range: 0-1), of semi-unsupervised topic labelling for
   each NFR and per word-list. Dashed line indicates the performance of a random classifier. This graph shows how well the
   semi-unsupervised topic labelling matched our manual annotations.}

@@

\subsection{Supervised labelling}
\label{sec:suplabelling}
Supervised labelling requires expert analysis of the correct class/label to assign to a topic. In our approach, we use the top-level NFRs in the ISO 9126 standard~\cite{iso9126} for our classes, but other taxonomies are also applicable.%In order to validate how effective these word-bag approaches to topic labelling would be we created a validation data set.

@@

\begin{figure}[t]
\centering
% \subfloat[MySQL]{
\includegraphics[width=0.45\textwidth]{figures/both-supervised}
% \label{fig:subfig1}
% }
% \subfloat[MaxDB]{
% \includegraphics[width=0.4\textwidth]{figures/maxdb-supervised}
% \label{fig:subfig2}
% }
\caption[]{ROC value for the best learner per label for MaxDB and MySQL. Values range from 0--1.  Dashed line indicates the performance of a random classifier.
%\todo[inline]{better discussion}
}
\label{fig:best-learn-per-tag}
\end{figure}

>>>>

Using our three word-lists (\textsf{exp1}, \textsf{exp2}, \textsf{exp3}), we labeled our topics with an NFR where there was a match between a word in the list and the same word somewhere in the distribution of words that constitute the topic.
A \emph{named topic} is a topic with a matching NFR label. Unnamed
topics occur where there is no such match, which may indicate either a lack of precision, or simply that this topic is not associated with non-functional requirements.
All experiments were run on MaxDB 7.500 and MySQL 3.23 data. LDA
extracted $20$ topics per period for each project.
% Is this good enough
This labelling is \emph{semi-unsupervised} because the corpus is not derived from 
the project being analyzed, and we did not label the project's topics
ourselves for a training set. The motivation behind this technique is that
because most software often addresses similar issues, thus we can use the
domain knowledge of software to label relevant topics.
%\todo[inline]{Neil does this explain the unsupervised aspect well enough?}

@@

% was best performing
For \textsf{exp1} the labels with the most topics
were
%labels, those with the most topics, 
\emph{correctness} (182 topics) and \emph{testability} (121). 
We did not see many results for \emph{usability} or \emph{accuracy}, which were associated with fewer than ten topics. 
We also looked for correlations between our labels: excluding double matches (self-correlation), our highest co-occurring terms were \emph{verifiability} with \emph{traceability}, and \emph{testability} with \emph{correctness} (76 and 62 matches, respectively).
% See the following sections for our error analysis.

@@

For \textsf{exp3}, we generally labelled more topics. 
As we mentioned, the word-lists are broad, so there are likely to be false-positives (discussed below). 
The most frequent label, 265 topics, was \emph{usability}, and the
least frequent label, 44 topics, was \emph{maintainability}. 
Common co-occurrences were \emph{reliability} with \emph{usability}, \emph{efficiency} with \emph{reliability}, and \emph{efficiency} with \emph{usability} (200, 190, and 150 topics in common, respectively).

@@

\begin{figure*}[t]
  \centering
 \includegraphics[width=0.8\textwidth]{figures/unsupervised-bar}
 \caption{Performance, ROC values (range: $0$--$1$), of semi-unsupervised topic labelling for
   each NFR and per word-list. Dashed line indicates the performance of a random classifier. This graph shows how well the
   semi-unsupervised topic labelling matched our manual annotations.}

@@

\subsection{Supervised labelling}
\label{sec:suplabelling}
Supervised labelling requires expert analysis of the correct
class/label to assign a label to a topic. In our approach, we use the top-level NFRs in the ISO 9126 standard~\cite{iso9126} for our classes, but other taxonomies are also applicable.%In order to validate how effective these word-bag approaches to topic labelling would be we created a validation data set.

@@

\begin{figure}[t]
\centering
% \subfloat[MySQL]{
\includegraphics[width=0.45\textwidth]{figures/both-supervised}
% \label{fig:subfig1}
% }
% \subfloat[MaxDB]{
% \includegraphics[width=0.4\textwidth]{figures/maxdb-supervised}
% \label{fig:subfig2}
% }
\caption[]{ROC value for the best learner per label for MaxDB and MySQL. Values range from $0$--$1$.  Dashed line indicates the performance of a random classifier.
%\todo[inline]{better discussion}
}
\label{fig:best-learn-per-tag}
\end{figure}
